### 2024-11-25 Manuscript/main_ecography_R1.tex
Update main_ecography_R1.tex

\textit{We have a data of bird traits for native species in Hawaii through time before and after 1500.
We want to know how anthropogenic stresses (hunting, invasive species, land use change) have affected the trait diversity in native Hawaiian birds.}

@@

@@

\section{Conclusion}
Different ecological and evolutionary processes or mechanisms do not always results in different patterns.
Our results based on simulations and empirical data suggest that the same data can be interpreted differently depending on the choice of trait space occupancy metric (\textit{aka} disparity, dissimilarity or functional diversity metrics).
Different metrics are designed to capture different aspects \citep{guillerme2020shifting,mammola2021concepts} but also perform better or worse at their designed task depending on the data, the mechanism or/and process of interest.
Using space occupancy metrics for describing functional diversity is tricky.
This is because the metrics have properties that can be counter intuitive based on the data at hand.
And also because functions of ecosystems or organisms and niches within it are hard to capture/understand/define.
This means that measuring functional diversity is based on both the definition of the metric and the function of interest and thus cannot be served by a one-fits-all metric.
In other words, it is important to choose a disparity/dissimilarity/functional diversity metric depending on the question and the data at hand rather than as a default option or solely based on a previous inspiring publication.
We suggest caution when summarising patterns in observed data and propose a pipeline and tools for researchers to help understand how their pattern (often stemming from multidimensional data) can vary intuitively or not depending on the process and mechanism of interest.

>>>>

\textit{We have data of bird traits for native species in Hawaii through time (e.g. before and after human colonisation of the archipelago).
We want to know how anthropogenic stresses (e.g. hunting, invasive species, land use change) have affected the trait diversity of native Hawaiian birds.}

@@

%TG: TODO: check the pre-1500 story from email from Tom and Maria

@@

\section{Conclusion}
Different ecological and evolutionary processes or mechanisms do not always results in different patterns.
Our results based on simulations and empirical data suggest that the same data can be interpreted differently depending on the choice of trait space occupancy metric (\textit{aka} disparity, dissimilarity or functional diversity metrics).
Different metrics are designed to capture different aspects \citep{guillerme2020shifting,mammola2021concepts} but also perform better or worse at their designed task depending on the data, the mechanism or/and process of interest.
Using space occupancy metrics for describing functional diversity is tricky.
This is because the metrics have properties that can be counter intuitive based on the data at hand.
And also because functions of ecosystems, or the organisms and niches within them, are hard to capture/understand/define.
This means that measuring functional diversity is based on both the definition of the metric and the function of interest and thus cannot be served by a one-fits-all metric.
In other words, it is important to choose a disparity/dissimilarity/functional diversity metric based on the question and the data at hand rather than as a default option or solely based on a previous inspiring publication.
We suggest caution when summarising patterns in observed data and propose a pipeline and tools for researchers to help understand how their pattern (often stemming from multidimensional data) can vary intuitively or not depending on the process and mechanism of interest.
